\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-13 manuscript.Rmd
EFA Plot updated

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci)
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

@@

p1 <- ggplot2::ggplot() + ggplot2::annotation_custom(grid::rasterGrob(img1,
                                                                      width=.4,
                                                                      height=.8),
                                                     -Inf, Inf, -Inf, Inf)+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
        #text=element_text(family = "Helvetica"))

EFAplot.1 <- plot_grid(
 p1, residual.plot,
  labels = "AUTO",
  align="h",
  ncol = 1,
  label_size = 15,
  label_fontfamily = "Arial",
  label_fontface = "plain",
  label_y = .99,
  label_x = .02,
 rel_heights = c(1.5,1)
)

ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 4, height =8, dpi = 600, bg ="white")

>>>>

```{r pacman, eval=FALSE, include=FALSE}
#You need to run this chunk 1X in your system 
#install.packages("pacman")#Run this if you don't have pacman installed.
pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci,networkD3, webshot)
webshot::install_phantomjs()
pacman::p_install_gh("jthomasmock/gtExtras")
pacman::p_install_gh("crsh/papaja")
pacman::p_install_gh("masiraji/tabledown")
pacman::p_install_gh("crsh/citr")
devtools::install_github("unDocUMeantIt/koRpus")
koRpus::install.koRpus.lang(lang=c("en"))

@@

p1 <- ggplot2::ggplot() + ggplot2::annotation_custom(grid::rasterGrob(img1,
                                                                      width=.4,
                                                                      height=.8),
                                                     -Inf, Inf, -Inf, Inf)+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())

EFAplot.1 <- cowplot::plot_grid(
  NULL, residual.plot,
  labels = c("", "B"),
  align="h",
  ncol = 1,
  label_size = 15,
  label_fontfamily = "Arial",
  label_fontface = "plain",
  label_y = .99
)

EFAplot.2 <- cowplot::plot_grid(
  p1, EFAplot.1,
  labels = c("A",""),
  align="h",
  ncol = 2,
  label_size = 15,
  label_fontfamily = "Arial",
  label_fontface = "plain",
  label_y = .99,
  label_x = .02
)

ggsave("Manuscript.figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200, bg ="white")
